\Large Analyzing the Supreme Court Citation Network

### 2017-12-03 Tex/paper.tex
added theory regarding sociality

>>>>

\textbf{Sociality} Citations sent beget citations sent.  For each case that applies, there is likely a case that needs to be discussed in terms of why it does not apply. Justices often clarify not only those legal principles that apply, but often those that do not. When multiple lines of legal reasoning are drawn upon to justify a decision, often more are discussed in terms of their lack of applicability.

"1. The "overbreadth" doctrine is not applicable here. There is nothing in the record to indicate that § 28.04 will have any different impact on any third parties' interests in free speech than it has on appellees' interests, and appellees have failed to identify any significant difference between their claim that § 28.04 is invalid on overbreadth grounds and their claim that it is unconstitutional when applied to their signs during a political campaign. Thus, it is inappropriate to entertain an overbreadth challenge to § 28.04. Pp. 466 U. S. 796-803."

https://supreme.justia.com/cases/federal/us/466/789/

``No allegations of racial or class-based invidiously discriminatory animus are required to establish a cause of action under the first part of  1985(2). The statutory provisions now codified at § 1985 were originally enacted as § 2 of the Civil Rights Act of 1871, and the substantive meaning of the 1871 Act has not been changed. The provisions relating to institutions and processes of the Federal Government (including the first part of § 1985(2)) -- unlike those encompassing activity that is usually of primary state concern (including the second part of § 1985(2) and the part of § 1985(3) involved in Griffin, supra -- contain no language requiring that the conspirators act with intent to deprive their victims of the equal protection of the laws. Thus, the reasoning of Griffin is not applicable here, and, given the structure of § 2 of the 1871 Act, it is clear''

https://supreme.justia.com/cases/federal/us/460/719/
